Type-Safe Modular Parsing

### 2017-01-14 paper/sections/Discussion.tex
Typo.

As many syntactically extensible parsers, our approach also supports
modifying part of existing parsers, but in a type-safe way. We can
easily update existing parsing rules with new implementations, or
eliminate them in extended parsers. This can be useful in many
situations, including when conflicts or ambiguities arize when
composing languages.
As an illustration, suppose we have an untyped lambda abstraction case in a base parser as below. \inlinecode{pLam} parses a lambda symbol, an identifier, a dot and an expression in sequence. Some irrelevant details are omitted.

@@

Our approach does not depend on a particular parser combinator library
or parsing algorithm. We demonstrated that Packrat parsing has some
advantages and is suitable in a modular setting. However, under
certain circumstances or in other programming languages, it may not be
the best choice. One can use other parser combinator libraries as long
as th guidelines proposed in Section~\ref{sec:packrat} are met.

>>>>

As many syntactically extensible parsers, our approach also supports
modifying part of existing parsers, but in a type-safe way. We can
easily update existing parsing rules with new implementations, or
eliminate them in extended parsers. This can be useful in many
situations, including when conflicts or ambiguities arise when
composing languages.
As an illustration, suppose we have an untyped lambda abstraction case in a base parser as below. \inlinecode{pLam} parses a lambda symbol, an identifier, a dot and an expression in sequence. Some irrelevant details are omitted.

@@

Our approach does not depend on a particular parser combinator library
or parsing algorithm. We demonstrated that Packrat parsing has some
advantages and is suitable in a modular setting. However, under
certain circumstances or in other programming languages, it may not be
the best choice. One can use other parser combinator libraries as long
as the guidelines proposed in Section~\ref{sec:packrat} are met.
